Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index

### 2016-01-22 paper.tex
A few corrections to the bib file

% !TeX spellcheck = <none>
\documentclass{article}
% Change Hons to PhD, MAE, MPhil or MComm as appropraite
% Remove singlespace and singleside for final version.

%\usepackage{lipsum}
\usepackage{float}
\usepackage{gensymb}
\usepackage{natbib}
\usepackage{pdfpages}
\usepackage{listings}
\title{Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index}
\author{Elle Saber, Rob J Hyndman \& Di Cook}

\begin{document}

\pagenumbering{roman}

@@

\begin{equation}
\label{eq FFDI}
F=2.0 e^{-0.450 + 0.987 \ln(D)-0.0345H+0.0338T+0.0234V}
\end{equation}
where 
\begin{itemize}
	\item $D$: drought factor (Index)
	\item $H$: relative humidity (percent)
	\item $T$: temperature (degrees Celsius)
	\item $V$: Average wind velocity ($km/hr$)
\end{itemize}

@@

Assembling the datasets began with the meterological data from the WRF model. This data came in NetCDF form \citep{ncdf}. The dataset spanned all of Eastern Australian (Queensland, New South Wales \& Victoria) with daily observations over a 25 year period. This area, divided into 10km grids, contained 28675 gridpoints each of which had longitude, lattitude and weather variable values (temperature, wind speed, relative humidty, FFDI and drought factor) associated with it. Once the time component is taken into account, the original dataset contained over 200 million data points (28675 $\times$ 365 $\times$ 25 ).

@@

Regression splines are a method for modelling nonlinear data as a number of piecewise  polynomial functions. The points at which the functions join are called knots. For example when the functions join at $x=k$, $k$is known as a knot \citep{ruppert03}.

As a result the logistic model becomes
\begin{equation}
\label{eq logits}
\Pr(Y=1|X)=\frac{\exp(\sum_{k=1}^K f_k(x_k))}{1+\exp(\sum_{k=1}^K f_k(x_k)}
\end{equation}
where $Y$ denomtes fire occurence, $x_k$ denotes the $k^{th}$ predictor and each $f_k$ represents a penalized regression spline.

Regression splines can be subject to over fitting: where the fitted model adheres to the data too strongly and doesn't smooth out ~noise' enough. This results in great in-sample predictions but poor out-of-sample predictions. To prevent over fitting occurring we use an automated method that optimizes the number of knots by penalizing for non-smoothness; an overview of using penalized regression splines in this context is given by \citet{wood02}.

@@

% Appendices start here
\bibliographystyle{asa}

>>>>

% !TeX spellcheck = <none>
\documentclass[11pt,a4paper]{article}
% Change Hons to PhD, MAE, MPhil or MComm as appropraite
% Remove singlespace and singleside for final version.

\usepackage{float,fullpage}
\usepackage{gensymb}
\usepackage{natbib}
\usepackage{pdfpages}
\usepackage{listings}

\title{Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index}
\author{Elle Saber, Rob J Hyndman \& Di Cook}

\begin{document}
\maketitle

@@

\begin{equation}
\label{eq FFDI}
F=2.0 e^{-0.450 + 0.987 \ln(D)-0.0345H+0.0338T+0.0234V}
\end{equation}
where 
\begin{itemize}
	\item $D$: drought factor (Index)
	\item $H$: relative humidity (percent)
	\item $T$: temperature (degrees Celsius)
	\item $V$: Average wind velocity (\emph{km/hr})
\end{itemize}

@@

Assembling the datasets began with the meterological data from the WRF model. This data came in NetCDF form \citep{ncdf}. The dataset spanned all of Eastern Australian (Queensland, New South Wales \& Victoria) with daily observations over a 25 year period. This area, divided into 10km grids, contained 28675 gridpoints each of which had longitude, lattitude and weather variable values (temperature, wind speed, relative humidty, FFDI and drought factor) associated with it. Once the time component is taken into account, the original dataset contained over 200 million data points ($28675 \times 365 \times 25$).

@@

Regression splines are a method for modelling nonlinear data as a number of piecewise  polynomial functions. The points at which the functions join are called knots. For example when the functions join at $x=k$, $k$ is known as a knot \citep{ruppert03}.

As a result the logistic model becomes
\begin{equation}
\label{eq logits}
\Pr(Y=1|X)=\frac{\exp(\sum_{k=1}^K f_k(x_k))}{1+\exp(\sum_{k=1}^K f_k(x_k)}
\end{equation}
where $Y$ denomtes fire occurence, $x_k$ denotes the $k$th predictor and each $f_k$ represents a penalized regression spline.

Regression splines can be subject to over fitting: where the fitted model adheres to the data too strongly and doesn't smooth out `noise' enough. This results in great in-sample predictions but poor out-of-sample predictions. To prevent over fitting occurring we use an automated method that optimizes the number of knots by penalizing for non-smoothness; an overview of using penalized regression splines in this context is given by \citet{wood02}.

@@

% Appendices start here
\bibliographystyle{agsm}
